Refinements for open automata

### 2022-05-04 2021-Refinement/paper/refinementarticle.tex
add notion of Refusal actions
def refusal traces

\DeclareMathOperator{\dom}{dom}

@@

Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock. In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata , there might not be a deadlock reduction in the composed ones. The same problem may arise when two related automata are composed in the same hole of a third one.

@@

\begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
\end{lemma}
\TODO{example}

>>>>

\DeclareMathOperator{\dom}{dom}
\newcommand{\rightarrowdbl}{\rightarrow\mathrel{\mkern-14mu}\rightarrow}

\newcommand{\xrightarrowdbl}[2][]{%
  \xrightarrow[#1]{#2}\mathrel{\mkern-14mu}\rightarrow
}

@@

Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock. In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata, there might not be a deadlock reduction in the composed ones. The same problem may arise when two related automata are composed in the same hole of a third one.

@@

\TODO{
A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
Notion of Extension refinement. May be we need to introduce the notion of  refusal of
a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
has executed the trace $t$. \[X \in \bot_{A}(t) \Leftrightarrow \{\exists s. s_0  \xrightarrowdbl{t} s \wedge \forall a \in X. s \not{\xrightarrow{a}}    \}\] and replace deadlock reducing, under (3) by
\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] } 
\begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
\end{lemma}
\TODO{example}
